---
title: "Youtube Trending Videos"
author: "Jie Liu"
date: "10/9/2019"
output:
  rmdformats::readthedown:
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This dataset includes data of trending videos on Youtube (01/12/2017 - 31/05/2018).<br/>

There are 16 variables in total.<br/>
Numeric:<br/>
views, likes, dislikes, comment_count<br/>
Categorical:<br/>
channel_title, category_id, tags, comments_disabled, ratings_disabled, video_error_or_removed<br/>
Time:<br/>
trending_date, publish_time<br/>
Other:<br/>
video_id, title, thumbnail_link, description<br/>

Each video may be put on the trending list more than once.<br/>
<br/>


# Thinking before Analysis

Since each video can show up several times in this dataset, lots of repetitive information exists. Moreover, all the numeric variables are cumulative, which means certain data processing methods are needed for the growth analysis concerning these variables.
<br/><br/>


# How to Be Trending

In my opinion, the value of each video follows this equation:<br/>
value = number of views * view duration.<br/>

Trending list is to provide users with the hottest videos in the past period (here we use a day), which can help those popular videos obtain more attention. Therefore, cumulative views and views growth rate are two important parameters to determine whether a video could be put on the trending list or not. The following analysis will focus on relationships between different independent variables and the number of views.
<br/><br/>


# Data Processing
## Read data and load packages
```{r, message=FALSE}
library(tidyverse)
library(lubridate)
youtube_orig <- read.csv("~/courses/mod1/intro_ba/team/youtube1.csv")
youtube <- youtube_orig
```

## Select the first trending data for each video (to avoid time-series influence)
```{r}
youtube_first_trending <- youtube %>%
  group_by(video_id) %>%
  mutate(first_trending = min(ydm(trending_date))) %>%
  filter(ydm(trending_date) == first_trending) %>%
  separate(publish_time, c("date","time"), sep="T") %>%
  filter(date>="2017-12-01") %>%
  dplyr::select(video_id, trending_date, date, time,title, channel_title, category_id, views,likes, dislikes, comment_count,tags) %>%
  distinct()
```
<br/>


# Two-sample T-Test
## Video Views at Weekends vs. Weekdays
H0: Trending videos have the same number of views during weekdays and weekends.<br/>
H1: Trending videos have different numbers of views during weekdays and weekends.
```{r}
youtube_ttest <- youtube_first_trending %>%
  mutate(week_day = weekdays(ymd(date))) %>%
  mutate(weekend=ifelse((week_day=="Saturday" | week_day=="Sunday"),1,0))

t.test(youtube_ttest$views ~ youtube_ttest$weekend,
       alternative = "two.sided", var.equal = TRUE)
```
## Summary
The t-test has a p-value of 0.566, which is far larger than 0.05, the pre-decided significance level. Therefore, the H0 can't be rejected, and trending videos tend to have the same number of views during weekday and weekend.
<br/><br/>


# Anova Test
## Video Views and Category ID
H0: Trending videos have the same number of views across different categories.<br/>
H1: Trending videos have different numberd of views across different categories.
```{r}
categoryTest <- aov(data = youtube_first_trending, views~as.factor(category_id))
summary(categoryTest)
TukeyHSD(categoryTest)
```
## Summary
The result of the ANOVA test shows a p-value that is greatly smaller than 0.05, the pre-decided significance level. Therefore, the H0 should be rejected, and trending videos tend to have different numbers of views across different categories.<br/>

Moreover, the TukeyHSD test indicates the exact differences in video views between pairwise groups. Category_10 (music) tends to have the most number of views, while category_25 (news & politics) tends to have the least.
<br/><br/>


# Regression Model
## Relationship between video views and number of tags
\[Views\ = \beta_0\ + \beta_1\ * Num\ of\ Tags\]
\[H_0: \beta_1\ = 0\] 
\[H_1: \beta_1\ != 0\]
```{r}
youtube_tags <- youtube_first_trending %>% 
  mutate(tags = as.character(tags)) %>% 
  mutate(numTags = ifelse((tags == "[none]"), 
                          0, str_count(tags, "\\|")+1))

model_tags <- lm(data = youtube_tags, views~numTags)
summary(model_tags)
par(mfrow = c(2, 2))
plot(model_tags)
```

## Summary
The coefficient has a 0.011 p-value that is smaller than 0.05, the pre-decided significance level. Thus, the H0 should be rejected, and the number of tags for a video can positively influence its number of views.<br/>

However, the following plots show that residuals are not normally distributed, and the r-square is only 0.001261. The F-statistic is 6.469, which also means this model is not a good fit to the dataset.
<br/><br/>


# Revised Regression Model
## Use music and news category as dummy variables
\[Views\ = \beta_0\ + \beta_1\ * Num\ of\ Tags\ + \beta_2\ * Dummy_{music}\ +\beta_3\ *\ Dummy_{news}\]
\[H_0: \beta_1\ = 0,\ \beta_2\ = 0,\ \beta_3\ = 0\]
\[H_1: \beta_1\ != 0,\ \beta_2\ != 0,\ \beta_3\ != 0\]
```{r}
youtube_dummy <- youtube_tags %>% 
  mutate(music = ifelse(category_id == 10, TRUE, FALSE)) %>% 
  mutate(news = ifelse(category_id == 25, TRUE, FALSE))

model <- lm(data = youtube_dummy, views~numTags+music+news)
summary(model)
par(mfrow = c(2, 2))
plot(model)
```

## Summary
All three coefficients have p-values that are smaller than 0.05, the pre-decided significance level. Thus, the H0 should be rejected, and the number of tags and the music dummy has a positive impact on video views, while the news dummy has a negative one.<br/>

However, the following plots show that residuals are not normally distributed, and dummy variables cause a blank space in fitted values. The r-square is increased to 0.2879, and the F-statistic becomes 50.59, which means this revised model is a better fit than the original one.
<br/><br/>


# Limitations
1. This dataset doesn't include data of those videos falling out of the trending list, which can be utilized to determine the views threshold of the trending list.<br/>
2. This analysis assumes the trending list is daily updated, while it actually may be updated every 15 minutes. This proxy leads to inaccuracy.<br/>
3. The revised model still doesn't have a high r-square and F-statistic, which means further analysis is needed to explore the relationship.


